---
title: "Check projections based on parameters"
output: html_notebook
---

This workflow aims to test how different parameters affect the output of projection methods such as *t-SNE* and *UMAP*. 

We'll pull the **VISp/ALM SMARTer** dataset to run *R-tSNE* and *uwot*(UMAP) and save the output coordinates in a tibble, with different settings in each row and the output stored within the row as a data.frame within a list.column. It will be easily accessible to build a shiny gallery app. 


First, let's load the test data:

```{r 1 Retrieve data}
library(scrattch.io)
library(Matrix)

load("//allen/programs/celltypes/workgroups/rnaseqanalysis/yzizhen/SmartSeq_cells/V1_ALM/process_24411/select.markers.rda")

tome <- "//allen/programs/celltypes/workgroups/rnaseqanalysis/shiny/tomes/facs/mouse_V1_ALM_20180520/transcrip.tome"

# Load annotations
anno <- read_tome_anno(tome)

anno <- anno %>%
  # Remove outlier clusters
  dplyr::filter(cluster_id %in% 1:133)

all_samples <- read_tome_sample_names(tome)
all_genes <- read_tome_gene_names(tome)


# Load count data
counts <- read_tome_dgCMatrix(tome, "/data/exon")
rownames(counts) <- all_samples
colnames(counts) <- all_genes

# Filter for markers
counts <- counts[, select.markers]

counts <- t(counts)

# Filter for samples
counts <- counts[,anno$sample_name]

# log transform
norm_counts <- log2(counts + 1)

# convert to matrix for projection input
norm_counts <- as.matrix(norm_counts)

```

A quick glimpse at the data we've just loaded:

```{r 2 Glimpse data}

library(DataExplorer)

DataExplorer::introduce(anno)
DataExplorer::plot_intro(anno)
DataExplorer::plot_bar(anno, nrow = 2, ncol = 2)

```


```{r}

```

